Case study validations of automatic bullet matching

### 2018-10-06 index.Rmd
tank rash bullets, added some conclusions

h44nest <- h44nest %>% filter(bullet1=="I") %>%  mutate(
  # sam_ccf = data %>% purrr::map_dbl(.f=function(d) {
  #   scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$ccf)
  #   max(scores)
  # }),
  sam_rf = data %>% purrr::map_dbl(.f=function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore)
    max(scores)
  })
  )
h44nest <- h44nest %>% 
  mutate(
    barrel2 = factor(barrel2, levels =c(1:10, "Unknown")),
    bullet1 = factor(bullet1, levels=rev(c("K", "O","L", "P",
                                           "J",
                                         "H", "I", "Y", "G",
                                         "E", "U", "X", "F", 
                                         "T", "S"))),
    bullet2 = factor(bullet2, levels=c(1:2, rev(levels(bullet1))))
  )
h44 <-  h44nest %>%
  ggplot(aes(y = bullet1, x = bullet2, 
             fill = sam_rf)) + 
  geom_tile(size=1) + 
  facet_grid(.~barrel2, space="free", scales = "free") +
  ylab("Questioned bullets") + 
  xlab("Testfires from barrels 1 to 10 (left), questioned bullets (right)") +
  scale_fill_gradient2("RF score ", low="darkgrey", 
                       high="darkorange", midpoint=0.35, limits=c(0,1)) + 
  scale_colour_manual("same source", values="darkorange") +

@@

>>>>

h44nest <- h44nest %>%  mutate(
  sam_ccf = data %>% purrr::map_dbl(.f=function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$ccf)
    max(scores)
  }),
  sam_rf = data %>% purrr::map_dbl(.f=function(d) {
    scores <- bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore)
    max(scores)
  })
  )
h44nest <- h44nest %>% 
  mutate(
    barrel2 = factor(barrel2, levels =c(1:10, "Unknown")),
    bullet1 = factor(bullet1, levels=rev(c("K", "O","L", "P",
                                           "J",
                                         "H", "I", "Y", "G",
                                         "E", "U", "X", "F", 
                                         "T", "S"))),
    bullet2 = factor(bullet2, levels=c(1:2, rev(levels(bullet1))))
  )
h44 <-  h44nest %>%
  ggplot(aes(y = bullet1, x = bullet2, 
             fill = sam_rf)) + 
  geom_tile(size=1) + 
  facet_grid(.~barrel2, space="free", scales = "free") +
  ylab("Questioned bullets") + 
  xlab("Testfires from barrels 1 to 10 (left), questioned bullets (right)") +
  scale_fill_gradient2("RF score ", low="darkgrey", 
                       high="darkorange", midpoint=0.35, limits=c(0,1)) + 
  scale_colour_manual("same source", values="darkorange") +

@@

# Appendix

\autoref{fig:tankrash} shows an overview of all lands of bullets in the Hamby-44 with major deficiencies, such as 'tank rash' or extreme pitting (holes caused by direct contact with burning gun powder).
```{r tankrash, fig.cap="Overview of bullet lands with prominent deficiency such as tank rash or extreme pitting in the Hamby-44 study.", fig.width=4, fig.height = 2, out.width='47.5%', fig.subcap=c("Br1-B1-L6", "Br2-B2-L5", "Br3-B1-L5", "Br8-B1-L6", "Br8-B2-L2", "Br8-B2-L6", "Unk-E-L6", "Unk-I-L6"), fig.align="middle", fig.ncol=2}
knitr::include_graphics(
  c('./images/B1-B1-L6.png', './images/B2-B2-L5.png',
    './images/B3-B1-L5.png', './images/B8-B1-L6.png',
    './images/B8-B2-L2.png', './images/B8-B2-L6.png',
    './images/NA-BE-L6.png', './images/NA-BI-L6.png')
)

Three lands across the two known bullets of barrel 8 are affected. This is the likely cause for the low scores for barrel 8 in \autoref{fig:h44}.

### Limitations
All of the studies involve the same firearm. We see some variations in scores across different models of Rugers. Likely, we are going to see even bigger variations with different brands of firearms, where there might be different number of lands of different lengths. We also know \cite{???} that different firearms mark differently well. Rugers are among the firearms that mark very well, so we would correspondingly expect to see lowered similarity scores for other firearms. The matching algorithm works on matching lands. Barrels with polygonal rifling, such as Glocks, do not introduce well defined lands on bullets, which makes an application of the matching algorithm impossible.

XXX Should we include some Sig Sauer matches?
